\texttt{Taxonomic supertree construction with}\texttt{\emph{ Incertae sedis}}\texttt{ taxa}

### 2018-04-19 doc/incertae_sedis.tex
more minor

\subsection{label{subsec:Placement}Placement}

@@

\subsection{Case 2: A nested emph{incertae sedis} clade}

@@

\subsection{Case 3: Placement of one incertae sedis taxon within
another.}

@@

\section{Handling emph{incertae sedis} taxa in the propinquity
pipeline}

>>>>

\subsection{Placement}\label{subsec:Placement}

@@

\subsection{Case 2: A nested \emph{incertae sedis} clade}

@@

\subsection{Case 3: Placement of one \emph{incertae sedis} taxon within
another.}

@@

\section{Handling \emph{incertae sedis} taxa in the propinquity
pipeline}
